Data Specialization for a Staged Lambda Calculus

### 2015-02-24 paper/figures/splitting-overview.tex
redo syntactically-separated-term overview figure to look better

\textbf{Syntactically Separated Term with Stage \bbtwo\ Output:}

\hspace{2em} Construction: $\pipeS p l r$, where

	\hspace{4em} $p$ is the {\em precomputation}, a monostage term representing the stage \bbone\ part of the program

	\hspace{4em} $l.r$ is the {\em resumer}, a monostage term representing the stage \bbtwo\ part of the program

\hspace{2em} Evaluation Form: $\sepredtwo {\pipeS p l r} q$, where

	\hspace{4em} $\pipeS p l r$ is the syntactically separated term to be evaluated

	\hspace{4em} $q$ is the resulting residual, a monostage term representing remaining stage \bbtwo\ work

\hspace{2em} Evaluation Rule: $\sepredtwo {\pipeS p l r} {[b/l]r}$, where $b$ (called the {\em boundary value}) is generated by $\reduce p b$

\textbf{Syntactically Separated Term with Multistage Output:}

\hspace{2em} Construction: $\pipeM c l r$, where

	\hspace{4em} $c$ is the {\em combined result}, a monostage term representing the stage \bbone\ part of the program

	\hspace{4em} $l.r$ is the {\em resumer}, a monostage term representing the stage \bbtwo\ part of the program

\hspace{2em} Evaluation Form: $\sepredone {\pipeM c l r} {\mval i q}$, where

	\hspace{4em} $\pipeM c l r$ is the syntactically separated term to be evaluated

	\hspace{4em} $\mval i q$ is the resulting masked value (defined below)

\hspace{2em} Evaluation Rule: $\sepredone {\pipeM c l r} {\mval i {[b/l]r}}$, where $b$ (also called the {\em boundary value}) is generated by $\reduce c {\tup{i,b}}$

\textbf{Masked Values:}

\hspace{2em} Construction: $\mval i q$, where

	\hspace{4em} $i$ is the {\em immediate result}, a monostage value representing the stage \bbone\ result

	\hspace{4em} $q$ is the {\em residual}, a monostage term representing stage \bbtwo\ work left to do

>>>>

\textbf{Syntactically Separated Term with Stage \bbtwo\ Output ---
$\pipeS p l r$}
\begin{enumerate}
\item[] Precomputation $p$ is a monostaged term containing the program's
first-stage computations.
\item[] Resumer $l.r$ is a monostaged term containing the program's 
second-stage computations.
\item[] Evaluates via $\sepredtwo {\pipeS p l r} q$, where the resulting
residual $q$ is a monostaged term containing the remaining second-stage
computations.
\item[] $\sepredtwo {\pipeS p l r} {[b/l]r}$, where $b$ (the boundary value) is
generated by $\reduce p b$.
\end{enumerate}

\textbf{Syntactically Separated Term with Multistage Output ---
$\pipeM c l r$}
\begin{enumerate}
\item[] Combined result $c$ is a monostage term containing the program's
first-stage computations.
\item[] Resumer $l.r$ is a monostage term containing the program's 
second-stage computations.
\item[] Evaluates via $\sepredone {\pipeM c l r} {\mval i q}$, where 
$\mval i q$ is the resulting masked value (defined below).
\item[] $\sepredone {\pipeM c l r} {\mval i {[b/l]r}}$, where $b$ (the boundary
value) is generated by $\reduce c {\tup{i,b}}$.
\end{enumerate}

\textbf{Masked Values ---
$\mval i q$}
\begin{enumerate}
\item[] Immediate result $i$ is a monostaged value representing the first-stage
result.
\item[] Residual $q$ is a monostaged term representing the second-stage work
left to do.
\end{enumerate}
